### 2020-02-23 manuscript/ERL_global_C_review.Rmd
minor

*Background.* The fate of Earth’s climate closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate through their influential role in the global carbon (C) cycle. Synthetic understanding of global forest C cycles is needed to constrain model estimates of forest feedbacks to climate change and to more accurately quantify the influence of land use decisions on climate.

>>>>

*Background.* *The fate of Earth’s climate closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate through their influential role in the global carbon (C) cycle. Synthetic understanding of global forest C cycles is needed to constrain model estimates of forest feedbacks to climate change and to more accurately quantify the influence of land use decisions on climate.*
